A unified pseudo-$C_\ell$ framework

### 2018-09-08 doc/Paper/main.tex
modified acknoweldgements to conform with PB guidelines

\subsection*{Acknowledgements}
  We would like to thank Rupert Allison, Scott Dodelson, Jo Dunkley, Franz Elsner, Boris Leistedt, Francois Lanusse, Thibaut Louis, Mathew Madhavacheril, Sigurd N\ae ss, Hiranya Peiris, Naomi Robertson and Ben Thorne for useful comments and discussions. DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council (STFC) through an Ernest Rutherford Fellowship, grant reference ST/P004474/1. This research used resources of the National Energy Research Scientific Computing Center (NERSC), a U.S. Department of Energy Office of Science User Facility operated under Contract No. DE-AC02-05CH11231.

@@

  \input{desc-tex/ack/standard}

>>>>

\subsection*{Acknowledgements}
  This paper has undergone internal review in the LSST Dark Energy Science Collaboration. The internal reviewers were Scott Dodelson, Francois Lanusse and Boris Leistedt. Besides them, we would like to thank Rupert Allison, Jo Dunkley, Franz Elsner, Daniel Lenz, Thibaut Louis, Mathew Madhavacheril, Sigurd N\ae ss, Hiranya Peiris, Naomi Robertson and Ben Thorne for useful comments and discussions.

@@

  DA acknowledges support from the Beecroft trust and from the Science and Technology Facilities Council (STFC) through an Ernest Rutherford Fellowship, grant reference ST/P004474/1.
  \input{desc-tex/ack/standard}
